% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{multicol}
\usepackage{enumerate}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.4in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%C++
\newcommand{\CC}{C\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\tiny\bf +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}}
%C#
\newcommand{\CS}{C\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\scriptsize\bf \#}}
%-----------------------------------------------------------



\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Rick M. Sullivan}  & \\
503.867.6118 & rick@ricksullivan.net\\
1365 Bellomy Street& www.ricksullivan.net\\
Santa Clara, CA 95050 & www.github.com/Rsullivan00\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{description}
\item
	\ressubheading{Santa Clara University - University Honors College}{Santa Clara, CA}{Bachelor of Science in Computer Science and Engineering}{Sep. 2011 - Present}
	\begin{itemize}
		\resitem{GPA: 3.876}
		\resitem{Mathematics minor}
	\end{itemize}

\item
	\ressubheading{Central Catholic High School}{Portland, OR}{Salutatorian (2nd in class)}{2007 - 2011}
	\begin{itemize}
		\resitem{GPA: 4.39}
	\end{itemize}
\end{description}

\resheading{Work Experience}
\begin{description}
\item
	\ressubheading{Accenture Technology - Cisco Systems}{San Jose, CA}{Business and System Integration Analyst}{Summer 2014}
	\begin{itemize}
		\resitem{Contributed to a MEAN stack crowdsourcing application (MongoDB, ExpressJS, AngularJS, NodeJS).}
		\resitem{Created an onboarding website for Accenture employees rolling on to Cisco teams.}
		\resitem{Participated in both Agile and Waterfall development methodologies.}
		\resitem{Tools used: Javascript (MEAN stack), SharePoint, Visio, Gimp, Rally.}
	\end{itemize}

\item
	\ressubheading{InComm Digital Solutions}{Portland, OR}{Software Engineering Intern}{Summer 2013}
	\begin{itemize}
		\resitem{Created documentation website for a web API that allows creating and managing gift cards.}
		\resitem{Created example front-end applications for endpoints of the API.}
		\resitem{Learned and participated in Agile development.}
		\resitem{Tools used: \CS, Visual Studio, Javascript, jQuery, CSS, SQL Server, ASP.NET. }	% Entity Framework?
	\end{itemize}

%\item
%	\ressubheading{Riverside Golf Course \& Country Club}{Portland, OR}{Pro-Shop Assistant}{2009 - 2012}
\end{description}

\resheading{Skills}

\begin{description}
\item[Languages:]
\CC, Javascript, Python.%\CS
\item[Relevant Coursework:]
\end{description}

\vspace*{-\baselineskip}
\begin{multicols}{3}
\begin{itemize}
\itemsep-2pt
\item Algorithms
\item Data Structures
\item Computer Architecture
\item Computer Networks
\item Embedded Systems
%\item Computer Forensics
\item Programming Languages
\item Compilers
\item Mobile App Development
\item OO Analysis and Design
\item Software Engineering
\item Operating Systems
\item Numerical Analysis 
\end{itemize}
\end{multicols}


\begin{description}
\item[Familiar With:]
Git, \LaTeX, HTML, CSS, LESS, Bootstrap, Vim, SQL.
\item[Operating Systems:]
Windows, *nix (Ubuntu, CentOS).
\end{description}

\resheading{Activities and Awards}

\begin{description}
\item[University Honors College]
Member of the Honors College at Santa Clara University.
\item[Upsilon Pi Epsilon]
Vice president of the Computer and Information honors society.
\item[Tau Beta Pi]
Member of the TBP engineering honors society.
\item[Santa Clara School of Engineering Dean's List]
\item[Santa Clara Provost Scholar]
Half-tuition scholarship for four years.
\end{description}


%\resheading{Things I Like}

%\begin{description}
%\item[Traveling] Spent the fall semester studying in Madrid, Spain, where I lived with a Spanish-speaking family.
%\item[Soccer] The Portland Timbers are the best team in the world.
%\item[Music] Huge fan of alternative, indie, rock, and electronic music. Favorite band: Dave Matthews Band.
%\end{description}

\end{document}
